---
title: "Quanteda_Chapter_1"
author: "Shreya Majumdar"
date: "2024-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quanteda Chapter 1

Install quanteda package and related ones.

```{r}
install.packages("topicmodels")
```

```{r}
install.packages("quanteda")
```

```{r}
install.packages("quanteda.textmodels")
install.packages("quanteda.textstats")
install.packages("quanteda.textplots")
```

Other packages:

```{r pressure, echo=FALSE}
install.packages("readtext")
```

Get other datasets

```{r}
install.packages("devtools") # get devtools to install quanteda.corpora
devtools::install_github("quanteda/quanteda.corpora")
```

```{r}
install.packages("spacyr")
install.packages("newsmap")
install.packages("seededlda")
```

Set of packages required for examples:

```{r}
require(quanteda)
require(quanteda.textmodels)
require(quanteda.textstats)
require(quanteda.textplots)
require(readtext)
require(devtools)
require(quanteda.corpora)
require(newsmap)
require(seededlda)
```

Quanteda has options to improve multithreading in parallelized operations. There is a default of 2 threads, but if RAM is large enough, can set higher. To set the number of threads, use this function:

```{r}
#change to 10 threads
quanteda_options("threads" = 10)
```

## R Basics

Concatenate strings with paste:

Note that when operations are applied on 2 vectors of the same length, performs like a dot product. When operations are applied 1 vector length n and 1 vector length 1, it is like scaling.

```{r}
vec_char <- c("apple", "banana", "mandarin", "melon")
vec_char2 <- paste(c("red", "yellow", "orange", "green"), vec_char)
print(vec_char2)
```

Label values

```{r}
#names allows you change the indexing from number based to other index
vec_num <- c(1, 5, 6, 3)
names(vec_num) <- vec_char
print(vec_num)
print(vec_num["apple"]) 

```

Create dataframe (in dataframe, not all values must be the same type)

```{r}
dat_fruit <- data.frame(name = vec_char, count = vec_num)
print(dat_fruit)
```

Num rows/cols:

```{r}
print(nrow(dat_fruit))
print(ncol(dat_fruit))
```

take subset:

```{r}
dat_fruit_sub <- subset(dat_fruit, count >= 5)
print(dat_fruit_sub)
```

Create matrix (all values must be the same type). Has a very strange format, keep that in mind (throws error is num values is not divisible):

```{r}
mat <- matrix(c(1, 3, 6, 8, 3, 5, 2, 7), nrow = 2)
print(mat)
```

Set row and column names (indices): --\> can use the updated names to call matrix values

```{r}
colnames(mat) <- vec_char
rownames(mat) <- c("bag1", "bag2") 
print(mat)
print(mat["bag1", ])
print(mat["bag1", "banana"])
```

Dimensions:

```{r}
print(dim(mat))
```

Marginals:

```{r}
print(rowSums(mat))
print(colSums(mat))
```
