---
title: "Quanteda_Chapter_1"
author: "Shreya Majumdar"
date: "2024-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quanteda Chapter 1

Sources:

\- <https://tutorials.quanteda.io/introduction/install/>

\- <https://rstudio.github.io/cheatsheets/quanteda.pdf>

## Package Installation

To use the Quanteda package, you need to install it. Quanteda works on top of the package TopicModels, so make sure to install it as well.

```{r}
install.packages("topicmodels")
```

```{r}
install.packages("quanteda")
```

Additionally, there are add-on packages that allow for additionally functionality in Quanteda:

```{r}
install.packages("quanteda.textmodels") #calculate text-based statistics
install.packages("quanteda.textstats") #fit supervised and unsupervised models
install.packages("quanteda.textplots") #create text-based visualizations
install.packages("quanteda.corpus") #manage text collection and metadata
install.packages("quanteda.tokens") #create and modify tokenized texts
install.packages("quanteda.dfm") #create and modify DFMs
install.packages("quanteda.fcm") #work with co-occurrence matrices
install.packages("newsmap")
install.packages("seededlda")
```

Here are some other packages that work well with Quanteda:

```{r pressure, echo=FALSE}
install.packages("readtext") #easy way to read text
install.packages("quanteda.textmodels") #build text-scaling and classification models
install.packages("spacyr") #package to implement NLP using the spaCy library
install.packages("quanteda.copora") #additional corpuses
install.packages("stopwords") #multilingual stopwords
```

Here are the set of packages required for examples:

```{r}
require(quanteda)
require(quanteda.textmodels)
require(quanteda.textstats)
require(quanteda.textplots)
require(readtext)
require(devtools)
require(quanteda.corpora)
require(newsmap)
require(seededlda)
```

## Multithreading

Quanteda has options to improve multithreading in parallelized operations. There is a default of 2 threads, but if RAM is large enough, can set higher. To set the number of threads, use this function:

```{r}
#change to 10 threads
quanteda_options("threads" = 10)
```

## R Basics

Here are some basic operations with numbers and strings that allow you to easily manipulate vectors. Note that when operations are applied on 2 vectors of the same length, performs like a dot product. When operations are applied 1 vector length n and 1 vector length 1, it is like scaling.

Concatenate strings with paste:

```{r}
vec_char <- c("apple", "banana", "mandarin", "melon")
vec_char2 <- paste(c("red", "yellow", "orange", "green"), vec_char)
print(vec_char2)
```

Label values:

```{r}
#names allows you change the indexing from number based to other index
vec_num <- c(1, 5, 6, 3)
names(vec_num) <- vec_char
print(vec_num)
print(vec_num["apple"]) 
```

Create dataframe (in dataframe, not all values must be the same type):

```{r}
dat_fruit <- data.frame(name = vec_char, count = vec_num)
print(dat_fruit)
```

Get number of rows or columns:

```{r}
print(nrow(dat_fruit))
print(ncol(dat_fruit))
```

Take a subset:

```{r}
dat_fruit_sub <- subset(dat_fruit, count >= 5)
print(dat_fruit_sub)
```

Create matrix (all values must be the same type). Mind the format, and the function throws an error if the number of values is not divisible by the number of rows:

```{r}
mat <- matrix(c(1, 3, 6, 8, 3, 5, 2, 7), nrow = 2)
print(mat)
```

Set row and column names (indices):

```{r}
colnames(mat) <- vec_char
rownames(mat) <- c("bag1", "bag2") 
print(mat)
print(mat["bag1", ])
print(mat["bag1", "banana"])
```

This is useful because you can use the updated names to retrieve matrix values.

Get dimensions of matrix:

```{r}
print(dim(mat))
```

Get or calculate marginals of a numerical matrix:

```{r}
print(rowSums(mat))
print(colSums(mat))
```
